{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-01-30 Paper/main.tex
Added Affidavit

>>>>

	\newpage
	\section{Affidavit}

	\vspace{2cm}
	"I hereby confirm that the work presented has been performed and
	interpreted solely by myself except for where I explicitly identified the
	contrary. I assure that this work has not been presented in any other
	form for the fulfillment of any other degree or qualification. Ideas
	taken from other works in letter and in spirit are identified in every
	single case."

	\vspace{2cm}
	Bonn, 11.02.2021 \hrulefill \\
	\hspace*{0mm}Jonghun Baek

	\vspace{2cm}
	Bonn, 11.02.2021 \hrulefill \\
	\hspace*{0mm}Jakob R. Juergens

	\vspace{2cm}
	Bonn, 11.02.2021 \hrulefill \\
	\hspace*{0mm}Jonathan Willnow
